Boosting Higgs Pair Production in the $bb\bar{b}\bar{b}$ Channel at the LHC with Multivariate Techniques

### 2015-07-13 paper/sec-analysis.tex
added comments
work on paper

Next, we show in
Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
comparing the resolved category (left) with the boosted category (right)
%
This is interesting since it determines the degree of boost that the two
Higgs candidates will have after non-resonant production.
%
In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the MVA in the next section.
%
For the boosted category the trend of the $m_{hh}$ distribution
is very different because of the selection, with the
distribution now peaking at much higher values.
%
In this case signal and background distributions
look reasonably similar.

>>>>

Another important kinematical distribution of this process is the invariant mass
of the di-Higgs system.
%
First of all because this is a direct measure of the boost of the system,
and also because in many BSM scenarios this distribution can be substantially
modified as compared to the SM case.
%
Next, we show in
Fig.~\ref{fig:mhh} the invariant mass distribution of the Higgs pairs,
comparing the resolved category (left) with the boosted category (right)
%
This is interesting since it determines the degree of boost that the two
Higgs candidates will have after non-resonant production.
%
In the resolved case, we see that the distribution
in $m_{hh}$ is rather harder for the signal as for the background,
and thus one expects that cutting in $m_{hh}$ would help signal
discrimination: we will verify this with the MVA in the next section.
%
For the boosted category the trend of the $m_{hh}$ distribution
is very different because of the selection, with the
distribution now peaking at much higher values.
%
In this case signal and background distributions
look reasonably similar.
%
Note that the $m_{HH}$ distribution as a kinematical
cut-off at $m_{HH}^{\rm min}=250$ GeV.
